Metal Mixing and Ejection in Dwarf Galaxies is Dependent on Nucleosynthetic Source

### 2019-03-07 individual_metals/main.tex

\begin{figure*}
\centering
\includegraphics[width=0.99\linewidth]{species_bar.png}\\
\includegraphics[width=0.99\linewidth]{species_bar_ISM.png}
\caption{Top: The mass fraction of each metal species in the \textit{full simulation box} contained in the halo, gas in the galaxy disk, and stars. Bottom: The mass fraction of species within \textit{the disk} alone in each phase of the ISM (bottom). The leftmost bar in each plot shows the sum of all metals.}
\label{fig:species_fractions}
\end{figure*}

@@

\begin{figure*}
\centering
\includegraphics[width=0.95\linewidth]{species_bar_sources.png}\\
\caption{The fraction of total mass in each metal species produced by each of the four possible nucleosynthetic channels in our model. These channels differ in both when metals are ejected, as determined by stellar evolution, and the phase of the ISM into which they are ejected.
We note that the minimal contribution from Type Ia SNe for the iron-peak elements is because  no older stellar population was initialized, so only 16 of them have exploded by the end of our 500~Myr simulation.}

@@

\begin{figure}
\centering
\includegraphics[width=0.95\linewidth]{SE_density.png}\\
\includegraphics[width=0.95\linewidth]{SE_z.png}
\caption{The volume-averaged gas number densities within 20~pc of a given event (top) and vertical position above/below the disk (bottom) within 1~Myr before the event.}
\label{fig:spatial distribution}
\end{figure}

@@

\begin{figure*}
\centering
\includegraphics[width=0.95\linewidth]{DD0390_element_by_element.png}
\caption{The numerical PDFs (solid histograms) and the associated log-normal + power-law fits (dashed lines) for a subset of the elements tracked in our simulation in each of the four gas phases defined in Section~\ref{sec:ejection}: CNM (dark blue), WNM (light blue), WIM (light orange), HIM (red), and all the gas in the ISM (black). For clarity, each distribution is normalized to the mode of the full-disk PDF (black) and is centered on the median value of the full-disk PDF. We note the vertical axis normalization is such that integrating over the shown PDF gives the mass fraction of that phase in the disk. Since the CNM dominates the mass fraction of our galaxy, the black curve is often obscured at low metal fractions.}
\label{fig:log-normal}
\end{figure*}

@@

\begin{figure*}
\centering
\includegraphics[width=0.95\linewidth]{O_Ba_distribution_evolution.png}
\caption{Time evolution of three different statistics for the full distributions of O (top) and Ba (bottom) in each phase of our simulation. The panels show log$_{10}$ of the median (left), the difference, in dex, between the mean and the median (middle), and the 90$^{\rm th}$ decile and 10$^{\rm th}$ decile difference in dex (right).}
\label{fig:phase-statistics}
\end{figure*}

@@

\begin{figure*}
\centering
\includegraphics[width=0.95\linewidth]{Half_AGB_Fraction_elements_s0.png}
\caption{The fraction of a given metal ejected through AGB winds at various times for a model of a single-age stellar population at $Z = 10^{-4}$ metal mass fraction, without continuing star formation. We only show a sample of some of the elements dominated most by AGB enrichment at late times. The horizontal line marks a 50\% contribution.}
\label{fig:agb evolution}
\end{figure*}

@@

\begin{figure}
\centering
\includegraphics[width=0.95\linewidth]{stellar_CNM_distance.png}
\caption{The separation (in dex) of each star's oxygen fraction from the median value of the CNM oxygen mass fraction PDF for the time within 1~Myr (our time resolution) of each star's formation time. The median deviation is given in the plot for stars formed after the initial star formation and enrichment period (120~Myr.)}
\label{fig:stars}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.475\linewidth]{density_PDF.png}
\includegraphics[width=0.475\linewidth]{density_PDF_volume_weighted.png}\caption{The mass-weighted (left) and volume weighted (right) density PDFs of our dwarf galaxy at an arbitrarily chosen time of 250~Myr. The total distribution is given in black, sub-divided by the contributions of the individual phases in the ISM.}
\label{fig:density_pdf}
\end{figure}

@@

\begin{figure*}
\centering
\includegraphics[width=0.95\linewidth]{O_Ba_resolution_study.png}
\caption{Resolution comparison of two lower resolution runs giving the log difference between the 90$^{\rm th}$ decile and 10$^{\rm th}$ decile in dex for the metal PDFS of O and Ba across all phases. Compare to Figure~\ref{fig:phase-statistics}.}
\label{fig:resolution-phase}
\end{figure*}

>>>>

\begin{figure*}
\centering
\includegraphics[width=0.99\linewidth]{species_bar}\\
\includegraphics[width=0.99\linewidth]{species_bar_ISM}
\caption{Top: The mass fraction of each metal species in the \textit{full simulation box} contained in the halo, gas in the galaxy disk, and stars. Bottom: The mass fraction of species within \textit{the disk} alone in each phase of the ISM (bottom). The leftmost bar in each plot shows the sum of all metals.}
\label{fig:species_fractions}
\end{figure*}

@@

\begin{figure*}
\centering
\includegraphics[width=0.95\linewidth]{species_bar_sources}\\
\caption{The fraction of total mass in each metal species produced by each of the four possible nucleosynthetic channels in our model. These channels differ in both when metals are ejected, as determined by stellar evolution, and the phase of the ISM into which they are ejected.
We note that the minimal contribution from Type Ia SNe for the iron-peak elements is because  no older stellar population was initialized, so only 16 of them have exploded by the end of our 500~Myr simulation.}

@@

\begin{figure}
\centering
\includegraphics[width=0.95\linewidth]{SE_density}\\
\includegraphics[width=0.95\linewidth]{SE_z}
\caption{The volume-averaged gas number densities within 20~pc of a given event (top) and vertical position above/below the disk (bottom) within 1~Myr before the event.}
\label{fig:spatial distribution}
\end{figure}

@@

\begin{figure*}
\centering
\includegraphics[width=0.95\linewidth]{DD0390_element_by_element}
\caption{The numerical PDFs (solid histograms) and the associated log-normal + power-law fits (dashed lines) for a subset of the elements tracked in our simulation in each of the four gas phases defined in Section~\ref{sec:ejection}: CNM (dark blue), WNM (light blue), WIM (light orange), HIM (red), and all the gas in the ISM (black). For clarity, each distribution is normalized to the mode of the full-disk PDF (black) and is centered on the median value of the full-disk PDF. We note the vertical axis normalization is such that integrating over the shown PDF gives the mass fraction of that phase in the disk. Since the CNM dominates the mass fraction of our galaxy, the black curve is often obscured at low metal fractions.}
\label{fig:log-normal}
\end{figure*}

@@

\begin{figure*}
\centering
\includegraphics[width=0.95\linewidth]{O_Ba_distribution_evolution}
\caption{Time evolution of three different statistics for the full distributions of O (top) and Ba (bottom) in each phase of our simulation. The panels show log$_{10}$ of the median (left), the difference, in dex, between the mean and the median (middle), and the 90$^{\rm th}$ decile and 10$^{\rm th}$ decile difference in dex (right).}
\label{fig:phase-statistics}
\end{figure*}

@@

\begin{figure*}
\centering
\includegraphics[width=0.95\linewidth]{Half_AGB_Fraction_elements_s0}
\caption{The fraction of a given metal ejected through AGB winds at various times for a model of a single-age stellar population at $Z = 10^{-4}$ metal mass fraction, without continuing star formation. We only show a sample of some of the elements dominated most by AGB enrichment at late times. The horizontal line marks a 50\% contribution.}
\label{fig:agb evolution}
\end{figure*}

@@

\begin{figure}
\centering
\includegraphics[width=0.95\linewidth]{stellar_CNM_distance}
\caption{The separation (in dex) of each star's oxygen fraction from the median value of the CNM oxygen mass fraction PDF for the time within 1~Myr (our time resolution) of each star's formation time. The median deviation is given in the plot for stars formed after the initial star formation and enrichment period (120~Myr.)}
\label{fig:stars}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.475\linewidth]{density_PDF}
\includegraphics[width=0.475\linewidth]{density_PDF_volume_weighted}\caption{The mass-weighted (left) and volume weighted (right) density PDFs of our dwarf galaxy at an arbitrarily chosen time of 250~Myr. The total distribution is given in black, sub-divided by the contributions of the individual phases in the ISM.}
\label{fig:density_pdf}
\end{figure}

@@

\begin{figure*}
\centering
\includegraphics[width=0.95\linewidth]{O_Ba_resolution_study}
\caption{Resolution comparison of two lower resolution runs giving the log difference between the 90$^{\rm th}$ decile and 10$^{\rm th}$ decile in dex for the metal PDFS of O and Ba across all phases. Compare to Figure~\ref{fig:phase-statistics}.}
\label{fig:resolution-phase}
\end{figure*}
